CASTRO: A New Compressible Astrophysical Solver. IV. Performance Portability

### 2018-11-05 gpus/paper.tex
more notes
more work

%\documentclass[12pt, preprint]{aastex}
\documentclass[preprint2,times]{aastex6}
%\documentclass[preprint,times]{aastex6}

@@

\citep{castro}

@@

>>>>

%\documentclass[12pt, preprint]{aastex}
\documentclass[twocolumn,times]{aastex62}
%\documentclass[preprint,times]{aastex6}

@@

is a compressible (radiation-)hydrodynamics simulation code built on
the AMReX adaptive mesh refinement framework \citep{castro,castro2,castro3}.  It 
includes full self-gravity using multigrid methods with isolated boundaries
\cite{katz:2016}, works with general equations of state \citep{zingalekatz}
and arbitrary nuclear reaction networks.

@@

Discuss frameworks vs.\ doing it outselves

Discuss OpenMP, OpenACC, and CUDA.
